Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-27 tex/ClementiBarba2020.tex
first stab at introduction

\documentclass[openacc]{rstransa} %%%%where rstrans is the template name

@@

PUT SOMETHING HERE. I DON'T GET WHAT WE ARE SUPPOSE TO PUT HERE, BUT THE GUIDELINES HAVE THIS

@@

\maketitle
% Body of paper.
\section{Background and methods}\label{sec:background}
\input{background}

>>>>

\documentclass{rstransa} %%%%where rstrans is the template name

@@

Some fields of research, particularly solid mechanics and computational fluid dynamics, have a long tradition of community consensus building and established practices for verification and validation of computational models. 
Such practices are uncommon in other fields of science, especially if they have more recently become computationally intensive.
Verification and validation also become increasingly difficult when the computational models arise from many levels of mathematical and physical modeling, representing a complex system. 
In recent years, science as a whole has come to be concerned with reproducibility and replication as a new front in the continual campaign to build confidence on published findings. 
Together with formal processes of uncertainty quantification, we have now three complementary ``axes'' to building trust in science.

@@

\maketitle
% Body of paper.

% continue Introduction

The lengths to which research communities should go to conduct activities in verification and validation, reproducibility and replication, and uncertainty quantification, are highly debated. 
Some journals require articles reporting on computational results to include proof of these activities, while most do not consider these aspects at all in their review criteria. 
In this paper, we tackle a sub-field of computational physics where tradition for these confidence-building activities is scant. 
The physical setting, excitation of resonance modes in nanostructures under an electromagnetic field, relies on multiple levels of modeling, while the experimental methods are complicated by the small length scales. 
We previously developed a computational model and software (called \pygbe) that has undergone code and solution verification, but a validation opportunity had remained elusive. 
Here, we present replication studies and a validation case based on published simulation and experimental results. 
Moreover, the studies in this paper were conducted under rigorous reproducibility practices, and all digital artifacts needed to reproduce every figure are shared in reproducibility packages available in a GitHub repository and archival services.

\section{Background and methods}\label{sec:background}
\input{background}
